% See Lection 2 page 11
% We need to make this plan without any adding specific dates. 
% just describe those steps

For this project we determined 6 stages:
\begin{enumerate}
    \item Business understanding
    \item Preliminary data analysis
    \item Data preparation
    \item Modeling
    \item Evaluation
    \item Deployment
\end{enumerate}

\bigskip

1. During \textit{Business understanding} phase will be performed analysis of problems which created the need for a project, prerequisites and conditions to satisfy business needs and requirements.

\bigskip

2. \textit{Preliminary data analysis} will contain estimation of data quality and quantity measurement to assess sufficiency for project requirements.

\bigskip

3. Selection, cleaning and (possibly) augmentation of data will be performed on \textit{Data preparation} stage to prepare data for modeling.

\bigskip

4. On the \textit{Modeling} stage various modeling techniques relevant to the task will be considered. After selection prototypes should be built (model test), their relevance be verified and if needed - these steps should be repeated. Then, chosen model(s) are to be built, used on the main data set.

\bigskip

5.  On \textit{Evaluation} stage model must be assessed for quality as problem solver, whether it satisfies business needs or there is need for one more iteration in search of appropriate model.

\bigskip

6. \textit{Deployment} of project is the final stage on which we preparing the project for integration with other systems such as robotic manipulator and shaker device and actual use, suitable for customer.



